---
title: "Naive Model Performance"
author: "Omprakash Samudrala"
date: "May 29, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = normalizePath("../.."))
```

<br>

## Naive Model

```{r message=FALSE, error=FALSE, warning=FALSE}
library(knitr)
library(caret)
source('./src/Models/Naive_Model.R')
```

### The erosion potential predicted by the Naive model (mean response of training data) was found to be **`r round(ErPot_Naive, 3)`**.

<br>

## Model Performance

```{r message=FALSE, error=FALSE, warning=FALSE}
library(Metrics)
## Compute RMSE and MAE over Test Data
RMSE_ErPot_Naive <- rmse(TstData$ErosionPotential,
                         rep(ErPot_Naive,nrow(TstData)))
MAE_ErPot_Naive <- mae(TstData$ErosionPotential,
                       rep(ErPot_Naive,nrow(TstData)))
```

### The root mean square error in predicting the erosion potential over the test data is **`r round(RMSE_ErPot_Naive, 3)`**. 

### The mean absolute error in predicting the erosion potential over the test data is **`r round(MAE_ErPot_Naive, 3)`**. The success metric as defined in the formal problem statement requires the mean absolute error in predicting erosion potential to be **< 0.05**. Hence the Naive model fails to meet the success metric.
