---
title: "ProjectPerformance"
author: "Omprakash Samudrala"
date: "May 8, 2018"
output: html_document
---

```{r echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = normalizePath(".."))
```

Load the Naive Model

```{r message=FALSE, echo=FALSE}
library(knitr)
source('src/Naive_model.R')
ggplot(data=TrgData,aes(x=ErosionPotential)) +
  geom_histogram(binwidth=0.02,fill="Magenta",color="Black")
```

Examine the Naive Model Performance - Erosion Potential Prediction

Determine the mean absolute error

```{r echo=FALSE}
NaiveResponse = c(rep(ErPot_Naive,nrow(TstData)))
AbsDeviationNaive = abs(TstData$ErosionPotential - NaiveResponse)
MeanAbsDeviationNaive = mean(AbsDeviationNaive)
```

The Erosion Potential as predicted by the Naive model has a mean absolute deviation of **`r MeanAbsDeviationNaive`** from the true value. 

The **Success Metric** required that this value be less than **0.05**. Hence the Naive model falls short of the success metric.

Need to explore additional models.
