---
title: "Random Forest Model Performance"
author: "Omprakash Samudrala"
date: "May 29, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = normalizePath("../.."))
```

<br>

## Random Forest Model

```{r message=FALSE, error=FALSE, warning=FALSE}
library(knitr)
library(caret)
source('./src/Models/RandomForest_Model.R')
summary(ErPot_RF)
plot(ErPot_RF)
```

<br>

## Model Performance

```{r message=FALSE, error=FALSE, warning=FALSE}
library(Metrics)

## Compute RMSE and MAE of Tree model over Test Data
## Compute RMSE and MAE of linear model over Test Data
RMSE_RF_Response = rmse(TstData$ErosionPotential, ErPot_RF_Predictions)
MAE_RF_Response = mae(TstData$ErosionPotential, ErPot_RF_Predictions)
```

### The root mean square error in predicting the erosion potential over the test data is **`r round(RMSE_RF_Response,3)`**. 

### The mean absolute error in predicting the erosion potential over the test data is **`r round(MAE_RF_Response,3)`**. The success metric as defined in the formal problem statement requires the mean absolute error in predicting erosion potential to be **< 0.05**. Hence the Random Forest model meets the success metric.

###**Random Forest** predictor is recommended for estimating the erosion potential of the VorTeq RPXs at any given operating condition.
